Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
Shorter.
MUHAHAH ORPHANS DEAD

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
other than HTTP, HTTPS, and DNS.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

@@

All participants will be asked to complete the same list of tasks, 
regardless of the censorship environment. 
Although every participant will attempt the same set of tasks, 
the difficulty of completing these tasks will vary based on 
their chosen censorship environment. 
The tasks are not all intended to be challenging to complete. 
Some may not even require the use or Tor Browser, 
depending on the environment.

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

@@

All participants will be given the same set of tasks, 
regardless of the censorship environment. 
Although every participant will attempt the same set of tasks, 
the difficulty of completing these tasks will vary based on 
their chosen censorship environment. 
The tasks are not all intended to be challenging to complete. 
Some may not even require the use or Tor Browser, 
depending on the environment.
